Fractional Decomposition Tree Algorithm: A tool for studying the integrality gap of Integer Programs

### 2022-01-22 FDT2020/response/response.tex

\response{Thank you for pointing this out. We corrected to say $\tilde{z}^i\in \mathcal{D}(S)$. We also added this observation at the beginning of section 2 that is cross-reference in the proofs: Any point $x\in [0,1]^n$ that is a convex combination of points in $\mathcal{D}(S)$, is also a convex combination of points in $\mathcal{D}(S) \cap [0,1]^n$}
\item p. 11, third paragraph: Same problem as previous bullet point.
\response{Fixed with referencing the Observation above.}
\item p. 13, top of page: Same problem.
\response{Fixed with referencing the Observation above.}
\item p. 24 and following, references: missing capitalization in a few entries

\end{itemize}

\subsection{Reviewer 2}

\subsubsection{Major Comments}
The computational results seem quite weak to me. The classic Feasibility Pump heuristic is known to produce solutions of fairly poor quality; it is designed primarily to produce feasible solutions to potentially difficult MIPs
quickly. On TAP and 2EC, the authors compare to problem-specific approximation algorithms that are not particularly designed to produce high quality solutions either.
\response{Our comparison of FDT to feasibility pump is to main showcase a use case of the algorithm and a direction that could be possibly explored. We are not offering FDT as a replacement for FP. We will add remarks that make this clear to the reader.

We respectfully disagree about the comment for 2EC since we use BOMC and turn it into an instance specific rounding algorithm for subtour elimination points. As presented in Figure 3, we don't settle for the worst-case upper bound of 3/2. Similarly, for TAP, FJ81 is the only rounding algorithm known for the solution of the CUT-LP. Again, we don't use the worst-case upper bound of 2 and use the instance specific gap provided by the algorithm. Also we remark that FDT is a generic algorithm that applies to any type of IP formulation, while BOMC and FJ81 only work for a certain type of formulation.}

\begin{enumerate}

### 2022-01-23 FDT2020/response/response.tex

\response{Here the goal is to establish that there is a $z\leq x^{(\ell+1)}$. For the coordinates of $x^{(\ell+1)}$ that are zero we show the proof. The other coordinates of $x^{(\ell+1)}$ are 1. So we just need to emphasize that all the $\tilde{z}_i \leq 1$. This is added now, an a reference to an observation we added (Observation 7)}.

\item (12,10) “maintainS”  \response{Fixed.}
\item (13,28) “Growing and Pruning THE FDT tree”
\response{Fixed.}
\item (14,12) “It is easy to check” <– you do this quite a bit. Please go through your paper and
pay attention to all the “easy to check”, “obvious”, “clearly” etc. If these things really are easy, then just state them and don’t waste space. However, if some observation is necessary, think about the clearest and most concise way to impart this observation to the reader, and then do that instead of telling the reader that it should be “easy”.

\response{Thank you for the reminder. We find several occurrences of trivially, obviously, easy to check and clearly.}

\item (14,12) “THE set $L'$” \response{Fixed.}
\item (14,25) “From THE leaves” 
\response{Fixed.}
\item (16,11-17) You should discuss why the intuitive approach of binarizing an LP (just split each variable into two binary variables and copy the respective column of the
constraint matrix) does not lead to the same or better result. Or maybe it does?
\response{We added this paragraph in the discussion of why $\{0,1,2\}$ problems are different from binary problems: Another approach to a $\{0,1,2\}$ problem could be to ``binarize'' the variables, but splitting each variable into two binary copies and solving the binary problem via FDT for binary IPs (Theorem \ref{FDTFull}). One potential issue that can arise by doing this is that the binary version of a problem might have a larger integrality gap compared to the one that allows larger multiplicity. One example of this is the 2EC problem considered in this section. As mentioned above, we have $g(\mbox{2EC})\leq \frac{3}{2}$, while $g(\mbox{2ECSS})\geq \frac{3}{2}$, where 2ECSS is a problem equivalent to 2EC but without any doubled edges allowed {CKKK08}.}

\item (19,14) “1Mb cache” – I looked up this CPU and it has 1MB of L2 cache. Note that
1Mb $\neq$ 1MB, and “cache” is quite an ambiguous term (there are several types of CPU
cache). Moreover, the amount of cache is a property of the CPU and is usually not
stated, so I would just not comment on it. If you must, give a correct capacity and
indicate the level of the cache. \response{We removed the cache amount. Thanks.}
\item (19,22-26) Is there no good benchmark set for TAP? If not, please mention that as
the reason why you study random instances. (It is not good practise in experimental
algorithmics to study random instances unless necessary.)
\item (20,22) One idea to consider and comment on: did you warm-start each computation of FDT? It seems to me that you could reuse the model that FDT solves in each
iteration – basically, you only change the objective and fix the variables which corresponds to changing lower/upper bounds, so you should be able to save time on
building / destroying the model. I’m not sure how much the pruning model can be reused. Either way, please comment on this idea. The idea was successful elsewhere,
e.g. https://arxiv.org/abs/1911.08636 
\item (21,10) Christofides’ algorithm is no longer the fastest https://arxiv.org/abs/2007.01409

### 2022-01-23 FDT2020/main-section.tex
addressed the comment on binrazing the 0,1,2 programs

In Section~\ref{sec:binaryfdt} our focus was on binary IPs. In this section, in an attempt to extend FDT to \{0,1,2\} problems we introduce an FDT algorithm for a 2-edge-connected multi-subgraph problem. Given a graph $G=(V,E)$ a multi-subset of edges $F$ of $G$ is a 2-edge-connected multi-subgraph of $G$ if for each set $\emptyset\subset U \subset V$, the number of edges in $F$ that have one endpoint in $U$ and one not in $U$ is at least 2. In 2EC, we are given non-negative costs on the edges of $G$ and the goal is to find the minimum cost 2-edge-connected multi-subgraph of $G$. We want to prove Theorem \ref{FDT2EC}.
\FDTEC*
We do not know the exact value for $g(\2ec)$, but we know $\frac{6}{5} \leq g(\2ec) \leq \frac{3}{2}$ \cite{alexander2006integrality,wolsey}. The FDT algorithm for 2EC is very similar to the one for binary IPs, but there are some differences as well. A natural thing to do is to have three branches for each node of the FDT tree, however, the branches that are equivalent to setting a variable to $1$, might need further decomposition. That is the main difficulty when dealing with $\{0,1,2\}$-IPs.

>>>>

In Section~\ref{sec:binaryfdt} our focus was on binary IPs. In this section, in an attempt to extend FDT to \{0,1,2\} problems we introduce an FDT algorithm for a 2-edge-connected multi-subgraph problem. Given a graph $G=(V,E)$ a multi-subset of edges $F$ of $G$ is a 2-edge-connected multi-subgraph of $G$ if for each set $\emptyset\subset U \subset V$, the number of edges in $F$ that have one endpoint in $U$ and one not in $U$ is at least 2. In 2EC, we are given non-negative costs on the edges of $G$ and the goal is to find the minimum cost 2-edge-connected multi-subgraph of $G$. We want to prove Theorem \ref{FDT2EC}.
\FDTEC*
We do not know the exact value for $g(\2ec)$, but we know $\frac{6}{5} \leq g(\2ec) \leq \frac{3}{2}$ \cite{alexander2006integrality,wolsey}\footnote{The recent result of \cite{KKO}  shows that $g(\2ec) \leq \frac{3}{2}-\epsilon$ for a tiny but constant $\epsilon >0$.}. The FDT algorithm for 2EC is very similar to the one for binary IPs, but there are some differences as well. A natural thing to do is to have three branches for each node of the FDT tree, however, the branches that are equivalent to setting a variable to $1$, might need further decomposition. That is the main difficulty when dealing with $\{0,1,2\}$-IPs.

Another approach to a $\{0,1,2\}$ problem could be to ``binarize'' the variables, but splitting each variable into two binary copies and solving the binary problem via FDT for binary IPs (Theorem \ref{binaryFDT}). One potential issue that can arise by doing this is that the binary version of a problem might have a larger integrality gap compared to the one that allows larger multiplicity. For instance, as mentioned above we have $g(\2ec)\leq \frac{3}{2}$ and  $g(\mbox{2ECSS})\geq \frac{3}{2}$, where 2ECSS is a problem equivalent to $\2ec$ but without any doubled edges allowed \cite{32gaptap}\footnote{In light of the recent paper of \cite{KKO} we now know that $g(\2ec)< g(\mbox{2ECSS})$.}
